\doublespacing
\setlength{\parindent}{1cm}

\par

Raga can be identified by various parameters. The particular choice of notes, Ascending and Descending sequences (known as arohana and avarohana pattern), nature of inflexion on different notes (gamaka/meend), characteristic phrases (pakad) all can be helpful to classify a raga (Raaga, 2019). These are further described below:

\begin{enumerate}
  \item Choice of Notes \par
  A rāga has a given set of notes (swaras), on a scale, ordered in melodies with musical motifs. The Indian tradition suggests a certain sequencing of how the musician moves from note to note for each rāga, in order for the performance to create a rasa (mood, atmosphere, essence, inner feeling) that is unique to each rāga. Theoretically, thousands of rāga are possible given 5 or more notes, but in practical use, the classical tradition has refined and typically relies on several hundred. For most artists, their basic perfected repertoire has some forty to fifty rāgas (Hindustani, 2019; Chordia and Ray, 2007). Each raga has a different set of swaras that constitutes it. There must be the notes of the rag.  They are the allowd swar.  This concept is similar to the Western solfege. There must also be a modal structure.  This is called that in North Indian music and mela in Carnatic music. There is also the jati.  Jati is the number of notes used in the rag. Rāga in Indian classic music is intimately related to tala or guidance about "division of time", with each unit called a matra (beat, and duration between beats) (Raaga, 2019). A rāga is not a tune, because the same rāga can yield an infinite number of tunes (Raaga, 2019).  A rāga is not a scale, because many rāgas can be based on the same scale. Each raga tends to have  a “Vadi” swara, a king swara on which maximum focus is given in a performance (Sharma and Bali, 2015).  It is also known as the most frequently occurring swara in a particular raga. It is followed by Samvadi (next in importance), then Anuvadi.  The swaras that are not allowed in a particular raga are known as Vivadi swaras (enemy notes).
  \par
  \item Arohana/Avarohana \par
  There must also be the ascending and descending sequence of notes.  This is called arohana /avarohana. Arohana and avarohana are the descriptions of how the raga moves.  The arohana, also called aroh or arohi, is the pattern in which a raga ascends the scale.  The avarohana, also called avaroh or avarohi, describes the way that the raga descends the scale.  Both the arohana and avarohana may use certain characteristic twists and turns.
  \par
  \item Pakad \par
  The pakad or swarup, is a defining phrase or a characteristic pattern for a raga.  This is often a particular way in which a raga moves; for instance the ``Pa M'a Ga Ma Ga'' is a tell-tale sign for Raga Bihag, or ``Ni Re Ga M'a'' is a telltale sign for Yaman.  Often the pakad is a natural consequence of the notes of arohana / avarohana (ascending and descending structures).  However, sometimes the pakad is unique and not implied by the notes of the arohana /avarohana.  It is customary to enfold the pakad into the arohana / avarohana to make the ascending and descending structures more descriptive (Raaga, 2019).
  \par
  \item Gamakas \par
  Gamakas are better known as ornamentations used in Hindustani music system. These are inflexions and rapid oscillatory movements taken across swaras (Sharma and Bali, 2015).
\end{enumerate}
\par

We now take one common raga as a running example and explain how the notes behave with respect to the above definitions and terms. Yaman emerged from the parent musical scale of Kalyan. Considered to be one of the most fundamental ragas in Hindustani tradition, it is thus often one of the first ragas taught to students. Yaman is a heptatonic (Sampurna) Indian classical raga of Kalyan Thaat. Yaman's Jati is a Sampurna raga.
\par
Arohana: Sa Re Ga Ma(Kori Ma/tivra Ma i.e. Ma\#) Pa Dha Ni Sa'
\par
Avarohana: Sa' Ni Dha Pa Ma ((Kori Ma/tivra Ma i.e. Ma\#)) Ga Re Sa
\par
The ascending Aaroha scale and the descending style of the avroha includes all seven notes in the octave (When it is Shadav, the Aroha goes like N,RGmDNS' , where the fifth note is omitted; Pa but the Avaroha is the same complete octave). All the scale notes (called swaras) in the raga are Shuddha, the exception being Teevra Madhyam or prati madhyamam (Hindustani, 2019). 
\par
\begin{flushleft}
  \textbf{Vadi and Samavadi} \par
\end{flushleft}
Vadi is G (ga) and Samvadi is N (ni). \par
\begin{flushleft}
  \textbf{Pakad or Chalan} \par
\end{flushleft}
Kalyan has no specific phrases or particular features, many musicians avoid Sa and Pa in ascend or treat them very weakly. You will often hear N0 R G M+ D N S' in ascent and S' N D M+ G R S in descent). Sa is avoided in beginning the ascend such as N0 R G M+ P D N S'.
To summarize the rules that make a raga: \par
A raga has at least 5 notes, including the Shadja. More than 5 is definitely ok. We can then add a further complexity, by choosing different swara in the ascent (Aaroha) and the descent (Avaroha). So the number of combinations can then be 5-5, 5-6,5-7,6-5,6-6,6-7,7-5,7-6 and 7-7. Five is Odhav, six is Shadhav and 7 is Sampoorna. So, an odhav-sampoorna raga will have 5 swar in the aaroha and 7 in the awaroha.
